---
title: "SCD-CovR_ML"
output: html_notebook
editor_options: 
  chunk_output_type: console
---

This is a short tutorial on how to run the SCD-CovR for my data. 

First I will check the empirical example (potato application)

#Loading the data
```{r}
load("G:/My Drive/R scripts/SCD-CovR/empirical example/empirical_results.Rdata")
```

Now let's dive into the existing code.
First it asks to install the package `RGCCA`. It can be done automatically by loading the script or you can use the following:

```{r}
install.packages("RGCCA")
```

The first chunck of code from the `potato_application.R` script is to load data from the personal folders of the author

```{r}
setwd("C:\\Users\\park\\Desktop\\paper2 writing for now\\oct02_new_simulation\\")

setwd("../potato_application/")
potato <- read.table("./potato.txt", sep = ",")

setwd("C:\\Users\\park\\Desktop\\paper2 writing for now\\paper2_multicore_results_complete\\")
Rcpp::sourceCpp("./sparseSCA.cpp")
Rcpp::sourceCpp("./updateW.cpp")

setwd("C:\\Users\\park\\Desktop\\paper2 writing for now\\oct02_new_simulation\\")
source("./evaluation_criteria.R")
source("./sscovr_looking_in.R")
source("./spcovrdata.R")
source("./cv_eigenvector_general.R")
source("./findLasso_sscovr_differentpenalties_adding_tryCatch_to_july10_version.R")
source("./findLasso_SCaDs.R")
source("./scad_cv.R")
source("./cv_eigenvector_sgcca.R")

# setting back the working directory
setwd("C:\\Users\\park\\Desktop\\Rstudio Github - Copy\\Project2_SPCovR\\paper2_writing\\")

```

Making the adjustments for the current github folder organization we will have:

```{r}
Rcpp::sourceCpp("./functions/sparseSCA.cpp")
Rcpp::sourceCpp("./functions/updateW.cpp")

source("./simulation study/compile evaluate results/evaluation_criteria.R")
source("./sscovr_looking_in.R")
source("./spcovrdata.R")
source("./cv_eigenvector_general.R")
source("./findLasso_sscovr_differentpenalties_adding_tryCatch_to_july10_version.R")
source("./findLasso_SCaDs.R")
source("./scad_cv.R")
source("./cv_eigenvector_sgcca.R")
```

